---
title: "Project 1"
author: "you"
output: pdf_document
date: "2023-10-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
# libraries
```

## Project objective

You will develop an automated pipeline to:  

a) pull financial market data, historical from your own MongoDB and current (yesterday) from a primary source like Yahoo Finance. 
b) munge and otherwise tidy the data. 
c) model market direction. 
d) create an pdf report. 
e) create an interactive shiny dashboard. 
f) insert data into a MongoDB. 



# Sections below TBD
## Define objectives of writeup


## Data (Munging - EDA stage)

### Data inport/gathering

### Data summarization

### Data visualization 

### Data preparation (tidying/engineering - human readable)

#### transformations - center/scale - dummy variables

#### correlation analysis

### Data preparation (tidying/engineering - machine readable)

#### transformations - center/scale - dummy variables

#### correlation analysis

## Modeling

## Evaluation - Discussion of what you saw/did

## Appendix ?
